Notes on Validated Model Counting \\ Version of \today

### 2022-08-27 doc/mc-notes.tex
Added additional ITE simplification
Split D4 from DSHARP
Further musings about number systems

@@

\begin{table}
  \caption{Recursive Definition of POGs and their Costs}
  \label{tab:pog}
%%A) Basic Operations\\
\begin{center}
\begin{tabular}{ccccc}
\toprule
  \makebox[15mm]{$P$}  & \makebox[30mm]{Restrictions} & \makebox[30mm]{$D(P)$} & \makebox[30mm]{$\interpset{P}$} & \makebox[25mm]{$\cost(P)$}\\
\midrule
  $\nil$  & None  & $\emptyset$    & $\emptyset$  & $0$\\
  $\tautology$        & None  & $\emptyset$    & $\uinterp$ & $1$ \\
$x_i$           & None  & $\{ x_i \}$    & $\{ \interp | \interp(x_i) = \tautology \}$ & $\cost(x_i)$ \\
$\neg P_1$      & None  & $\depend(P_1)$ & $\uinterp - \interpset{P_1}$ & $\oneminus\cost(P)$ \\
$P_1 \pand P_2$ & $\depend(P_1) \cap \depend(P_2) = \emptyset$ & $\depend(P_1) \cup \depend(P_2)$ & $\interpset{P_1} \cap \interpset{P_2}$
& $\cost(P_1) \cdot \cost(P_2)$\\
$P_1 \por P_2$  & $\interpset{P_1} \cap \interpset{P_2} = \emptyset$ &  $\depend(P_1) \cup \depend(P_2)$ &  $\interpset{P_1} \cup \interpset{P_2}$
& $\cost(P_1) + \cost(P_2)$\\
\bottomrule
\end{tabular}
\end{center}
%% B) Composite Operations\\
%% \begin{center}
%% \begin{tabular}{cc}
%% \toprule
%%   $P$           & Definition \\
%% \midrule
%% \makebox[30mm]{$\pite(P_1, P_2, P_3)$} & \makebox[40mm]{$[P_1 \pand P_2] \por [\neg P_1 \pand P_2]$}\\
%% \bottomrule
%% \end{tabular}
%% \end{center}
\end{table}

@@

\begin{table}
  \caption{Encodings of the ITE Operation}
  \label{tab:ite}
  \begin{center}
  \begin{tabular}{ccc}
    ITE Form & & Encoding \\
    \midrule
     $\ite(P_1, P_2, P_3)$ & $$ & $(P_1 \pand P_2) \por (\neg P_1 \land P_3)$ \\
     $\ite(\tautology, P_2, P_3)$ & $$ & $P_2$ \\
     $\ite(\nil, P_2, P_3)$ & $$ & $P_3$ \\
     $\ite(P_1, \tautology, \nil)$ & $$ & $P_1$ \\
     $\ite(P_1, \nil, \tautology)$ & $$ & $\neg P_1$ \\
     $\ite(P_1, P_2, \nil)$ & $$ & $P_1 \pand P_2$ \\
     $\ite(P_1, \nil, P_3)$ & $$ & $\neg P_1 \pand P_3$ \\
     $\ite(P_1, \tautology, P_3)$ & $$ & $\neg (\neg P_1 \pand \neg P_3)$ \\
     $\ite(P_1, P_2, \tautology)$ & $$ & $\neg (P_1 \pand \neg P_2)$ \\
  \end{tabular}
  \end{center}
\end{table}

>>>>

{\bf Example 1d}: Restrict the rational numbers of Example~1c to be of
the form $a\cdot 2^b\cdot 5^c$, where $a$, $b$, and $c$ are integers.
This class of numbers can exactly represent any value written in
base-10 decimal notation, and it is closed under addition and
multiplication.  It can therefore be used to exactly
encode the weights used in the weighted model counting track of the
Model Counting Competition, as well as any results that are to be
generated.  In terms of implementation, both $b$ and $c$ can be encoded
as fixed-length integers, leaving only $a$ requiring an
arbitrary-precision representation.  Manipulating numbers with this
representation could be simpler and more efficient than using full rational
arithmetic.

@@

\begin{table}
  \caption{Recursive Definition of POGs and their Costs}
  \label{tab:pog}
%%A) Basic Operations\\
\begin{center}
\begin{tabular}{ccccc}
\toprule
  \makebox[15mm]{$P$}  & \makebox[30mm]{Restrictions} & \makebox[30mm]{$D(P)$} & \makebox[30mm]{$\interpset{P}$} & \makebox[25mm]{$\cost(P)$}\\
\midrule
  $\nil$  & None  & $\emptyset$    & $\emptyset$  & $0$\\
  $\tautology$        & None  & $\emptyset$    & $\uinterp$ & $1$ \\
$x_i$           & None  & $\{ x_i \}$    & $\{ \interp | \interp(x_i) = \tautology \}$ & $\cost(x_i)$ \\
$\neg P_1$      & None  & $\depend(P_1)$ & $\uinterp - \interpset{P_1}$ & $\oneminus\cost(P)$ \\
$\pand \{ P_1, \ldots, P_k \}$ & $\depend(P_i) \cap \depend(P_j) = \emptyset$, $1\leq i < j \leq k$ & $\bigcup_{1\leq i \leq k} \depend(P_i)$ & $\bigcap_{1\leq i \leq k} \interpset{P_i}$
& $\prod_{1 \leq i \leq k} \cost(P_i)$\\
$P_1 \por P_2$  & $\interpset{P_1} \cap \interpset{P_2} = \emptyset$ &  $\depend(P_1) \cup \depend(P_2)$ &  $\interpset{P_1} \cup \interpset{P_2}$
& $\cost(P_1) + \cost(P_2)$\\
\bottomrule
\end{tabular}
\end{center}
%% B) Composite Operations\\
%% \begin{center}
%% \begin{tabular}{cc}
%% \toprule
%%   $P$           & Definition \\
%% \midrule
%% \makebox[30mm]{$\pite(P_1, P_2, P_3)$} & \makebox[40mm]{$[P_1 \pand P_2] \por [\neg P_1 \pand P_2]$}\\
%% \bottomrule
%% \end{tabular}
%% \end{center}
\end{table}

@@

\begin{table}
  \caption{Encodings of the ITE Operation}
  \label{tab:ite}
  \begin{center}
  \begin{tabular}{ccc}
    ITE Form & & Encoding \\
    \midrule
     $\ite(P_1, P_2, P_3)$ & $\;$ & $(P_1 \pand P_2) \por (\neg P_1 \land P_3)$ \\
     $\ite(\tautology, P_2, P_3)$ & $\;$ & $P_2$ \\
     $\ite(\nil, P_2, P_3)$ & $\;$ & $P_3$ \\
     $\ite(P_1, P_2, P_2)$  & $\;$ & $P_2$ \\
     $\ite(P_1, \tautology, \nil)$ & $\;$ & $P_1$ \\
     $\ite(P_1, \nil, \tautology)$ & $\;$ & $\neg P_1$ \\
     $\ite(P_1, P_2, \nil)$ & $\;$ & $P_1 \pand P_2$ \\
     $\ite(P_1, \nil, P_3)$ & $\;$ & $\neg P_1 \pand P_3$ \\
     $\ite(P_1, \tautology, P_3)$ & $\;$ & $\neg (\neg P_1 \pand \neg P_3)$ \\
     $\ite(P_1, P_2, \tautology)$ & $\;$ & $\neg (P_1 \pand \neg P_2)$ \\

  \end{tabular}
  \end{center}
\end{table}
